
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../images/")
library(rmarkdown)
```

## My (not so hot) take on R

I wasn't looking forward to learning R...  

When I started my first R class almost two years ago, I wasn't all that excited about it. I was more comfortable in SAS and had dabbled a bit in Python, and I was content with limiting my coding knowledge to those two languages. R just looked... ugly?  

After I got over my initial disgust toward the syntax, I realized that the same nasty looking syntax was surprisingly very easy to learn. The more capable I became as an R programmer, the more I realized that I could perform many of the same analyses and render the same plots that I could in SAS, only in much fewer lines of code and often with better graphics.

I especially appreciate the capability to create nicely formatted html pages as well as interactive graphics. Although I miss the visual appeal of a detailed and hierarchically formatted SAS proc step, I can finally say that I prefer R as my primary coding language because of its ease of use, flexibility, and intuitive (albeit ugly) syntax.

## Example R Markdown Output  

```{r example graphics}
plot(iris)
```


```{r render in console, eval = FALSE}
rmarkdown::render("C:\\Users\\autum\\Documents\\ST 558\\atbiggie.github.io\\_Rmd\\2021-09-07-MyTakeOnR.Rmd", output_format = "github_document", output_dir = "../atbiggie.github.io/_posts/", output_options = list(html_preview = FALSE))
```

