
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
getwd()
knitr::opts_knit$set(base.url = "https://github.com/atbiggie/atbiggie.github.io/blob/master/images/")
```

Looking back on my previous posts, not much has changed about my view on what data scientists do. As I've grown in my skillset and knowledge of different data-handling techniques, ways to access data, as well as how to create beautiful visualizations and presentations, I've been discovering what it FEELS like to be a data scientist. Reading about the difference between a statistician and a data scientist is one thing, but using new tools and learning to THINK like a data scientist is another thing. I'm excited to keep using the tools I've learned and continue exploring this growing field.  

Over the span of this semester, I have grown not only to view R as an intuitive language for data science, but as a language I will use for the rest of my career. It has easy syntax, it's well documented, and other coders are constantly sharing ways to do new things and analyze data. I think the value in R lies in the many different ways to present my work. R Markdown, Github pages, and ShinyApps provide so many possibilities for creating engaging reports and interactive presentations.  

Now that I've taken ST 558, I'll be looking for a job that allows me to use R frequently, or even as my main coding language. In addition, I'm excited to start using R for some personal projects outside of school, as well as to present data for other statistics classes.  

I'll keep you posted on what I create!  



```{r render in console, eval=FALSE, echo=FALSE}
rmarkdown::render("C:\\Users\\autum\\Documents\\ST 558\\atbiggie.github.io\\_Rmd\\2021-11-19-Course-Reflections.Rmd", output_format = "github_document", output_dir = "../atbiggie.github.io/_posts/", output_options = list(html_preview = FALSE))
```

